IMF and Benchmark Forecasts

### 2023-10-25 manuscript/manuscript.tex
change year-sampling: now depends on horizon -> real-time compatible

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={IMF and Benchmark Forecasts},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\newpage
\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule
expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
leave-one-out\_interval\_score & 0.112 & 0.123 & 0.123 \\ 
leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
\midrule
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule
expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
leave-one-out\_interval\_score & 0.257 & 0.257 & 0.276 \\ 
leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule
expanding window\_interval\_score & 0.448 & 0.737 & 0.590 \\ 
expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
leave-one-out\_interval\_score & 0.443 & 0.746 & 0.587 \\ 
leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
rolling window\_interval\_score & 0.451 & 0.739 & 0.591 \\ 
rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule
expanding window\_interval\_score & 0.495 & 1.044 & 0.800 \\ 
expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
leave-one-out\_interval\_score & 0.488 & 1.021 & 0.756 \\ 
leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
rolling window\_interval\_score & 0.494 & 1.041 & 0.779 \\ 
rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
\bottomrule
\end{longtable}

@@

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule
expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
leave-one-out\_interval\_score & 0.235 & 0.297 & 0.295 \\ 
leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
\midrule
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule
expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
leave-one-out\_interval\_score & 0.406 & 0.532 & 0.482 \\ 
leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule
expanding window\_interval\_score & 0.837 & 1.090 & 0.942 \\ 
expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
leave-one-out\_interval\_score & 0.833 & 1.083 & 0.933 \\ 
leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
rolling window\_interval\_score & 0.851 & 1.122 & 0.970 \\ 
rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule
expanding window\_interval\_score & 1.045 & 1.288 & 1.102 \\ 
expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
leave-one-out\_interval\_score & 1.030 & 1.292 & 1.109 \\ 
leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
rolling window\_interval\_score & 1.056 & 1.312 & 1.143 \\ 
rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
\bottomrule
\end{longtable}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={IMF and Benchmark Forecasts},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\newpage
\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
leave-one-out\_interval\_score & 0.112 & 0.123 & 0.123 \\ 
leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
leave-one-out\_interval\_score & 0.257 & 0.257 & 0.276 \\ 
leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.447 & 0.740 & 0.595 \\ 
expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
leave-one-out\_interval\_score & 0.443 & 0.746 & 0.587 \\ 
leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
rolling window\_interval\_score & 0.458 & 0.744 & 0.601 \\ 
rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.503 & 1.051 & 0.812 \\ 
expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
leave-one-out\_interval\_score & 0.488 & 1.021 & 0.756 \\ 
leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
rolling window\_interval\_score & 0.506 & 1.043 & 0.790 \\ 
rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
\bottomrule
\end{longtable}

@@

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
leave-one-out\_interval\_score & 0.235 & 0.297 & 0.295 \\ 
leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
leave-one-out\_interval\_score & 0.406 & 0.532 & 0.482 \\ 
leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 0.846 & 1.094 & 0.947 \\ 
expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
leave-one-out\_interval\_score & 0.833 & 1.083 & 0.933 \\ 
leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
rolling window\_interval\_score & 0.858 & 1.121 & 0.973 \\ 
rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule\addlinespace[2.5pt]
expanding window\_interval\_score & 1.063 & 1.297 & 1.113 \\ 
expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
leave-one-out\_interval\_score & 1.030 & 1.292 & 1.109 \\ 
leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
rolling window\_interval\_score & 1.075 & 1.313 & 1.150 \\ 
rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
\bottomrule
\end{longtable}
